Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-08-25 xrb2/paper.tex
add some references

Insert some stuff here about previous work on rotation

@@

\software{AMReX \citep{amrex_joss},
          Castro \citep{castro},
          GCC (\url{https://gcc.gnu.org/}),
          linux (\url{https://www.kernel.org/}),
          matplotlib (\citealt{Hunter:2007}, \url{http://matplotlib.org/}),
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          valgrind \citep{valgrind},
          VODE \citep{vode},
          yt \citep{yt}}

>>>>

Previous studies have found that rotation can have a significant affect on the flame's propagation. As the rotation rate increases, the Coriolis force whips the spreading flame up into a hurricane-like structure \citep{spitkovsky2002,cavecchi:2013}. The stronger Coriolis force leads to greater confinement of the hot accreted matter, leading to easier ignition of the flame \citep{art-2015-cavecchi-etal}.

Previous work has predicted that crustal heating is stronger a lower accretion rates and weaker at higher accretion rates, due to the effect of neutrino losses \citep{Cumming2006,johnston:2019}. In our models, we keep the crust at a constant temperature, so by increasing this temperature we can effectively increase the crustal heating and mimic the effects of lower accretion rates. A shallow heating mechanism of as yet unknown origin has been found necessary to reproduce observed properties of XRBs \citep{Deibel2015,Turlione2015,Keek2017}.

@@

\software{AMReX \citep{amrex_joss},
          Castro \citep{castro},
          GCC (\url{https://gcc.gnu.org/}),
          Jupyter \citep{Kluyver2016},
          linux (\url{https://www.kernel.org/}),
          matplotlib (\citealt{Hunter:2007}, \url{http://matplotlib.org/}),
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          valgrind \citep{valgrind},
          VODE \citep{vode},
          yt \citep{yt}}
